Refinements for open automata

### 2022-06-30 2021-Refinement/paper/refinementarticle.tex
Plan

@@

\section{a recuperer si on se rend compte que c'est utile}
When we will introduce refinements in Section \ref{sec:prelref}, setting an undefined variable will be considered a valid refinement, for instance a \(5\) bits register is a particular \(n\) bits register.

>>>>

The following of this article is organised as follows. 
We first review related works in Section~\ref{sec:sota}; then Section~\ref{sec:background} recalls the definition of open automata and defines their composition. 
We  then  define a refinement relation for open automata, first only considering two automata with the same set of holes in Section~\ref{sec:refinement} and generalize it to automataa with a different set of holes in Section~\ref{sec:holes} before proving basic properties of refinement in Section~\ref{sec:prop}; here we prove that refinement is a preorder and we focus on one composition property. 
Section~\ref{sec:ccl} concludes the paper.

@@

%\section{a recuperer si on se rend compte que c'est utile}
%When we will introduce refinements in Section \ref{sec:prelref}, setting an undefined variable will be considered a valid refinement, for instance a \(5\) bits register is a particular \(n\) bits register.
